A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-18 text/informal-overview.tex
Revising.

CSP, cross-stage persistence, is an important feature of \LTP.
It enables us to embed value at an outer stage into an inner stage.
$\%$ is dedicated to CSP in \LTP.
\AI{What should me mentioned here is that in MetaOCaml CSP is implicit but
in \LTP it's explicit.}
For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
\red{inner / outer は適切か?}
\AI{What is \(a\)?}
\AI{Is this explanation enough to understand the rest of the section?}

@@

% \LLF
\LLF is a simple system of dependent types introduced in \cite{attapl}.
\red{system / type system / calculus?}
It is based on Edinburgh LF\cite{harper1993framework}.
\AI{Can you remind me of differences between Edinburgh LF and \LLF?}
Therefore, \AI{``Therefore'' is used to show a logical consequence.} all constants and base types are declared in the signature.
The \LLF type theory generalizes simply typed lambda calculus
by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.  \AI{``dependent product'' vs. ``dependent function''.}

% Kind, Well-formed kind
In addition to ordinary typing rules like simply typed lambda calculus,
there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
Kinding rules and well-formed kinding rules are 
introduced in order to prohibit making illegal types such as $\textrm{Vect}\ \textrm{Bool}$.  \AI{Vect\ true may be a better example?}
For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under an environment $\G$.

% Type Equality
Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
For example, $\textrm{Vect}\ 7$ should be equivalent to $\textrm{Vect}\ (3+4)$
but they are not equivalent seemingly. Thus, we must define equivalence rules.
In \LLF, equivalence is expressed with a symbol of $\E$.
$\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
$\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
$\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.

>>>>

CSP, cross-stage persistence, is an important feature of \LTP.
It enables us to embed value at an outer stage into an inner stage.
In \LTP, CSP is written explicitly and $\%$ is a symbol dedicated to CSP
although MetaOCaml CSP is implicit and there is no symbol for CSP.
For example, $\lambda a:\I.\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x+\%_\alpha a))$
\red{inner / outer は適切か?}
\AI{What is \(a\)?}
\AI{Is this explanation enough to understand the rest of the section?}

@@

% \LLF
\LLF is a simple system of dependent types introduced in \cite{attapl}.
\red{system / type system / calculus?}
It is based on Edinburgh LF\cite{harper1993framework}.
\AI{Can you remind me of differences between Edinburgh LF and \LLF?}
Therefore, \AI{``Therefore'' is used to show a logical consequence.} all constants and base types are declared in the signature.
The \LLF type theory generalizes simply typed lambda calculus
by replacing the function type $\tau\to\sigma$ with the dependent function type $\Pi x:\tau.\sigma$.

% Kind, Well-formed kind
In addition to ordinary typing rules like simply typed lambda calculus,
there are kinding rules, well-formed kinding rules, term equivalence rules, type equivalence rules, and kind equivalence rules in \LLF.
Kinding rules and well-formed kinding rules are 
introduced in order to prohibit making illegal types such as $\textrm{Vector}\ \textrm{true}$.
For a well-formed type $\tau$, $\G \vdash \tau :: K$ means that $\tau$ has a kind $K$ under the environment $\G$ and 
for a well-formed kind $K$, $\G \vdash K$ means that $K$ is a well-formed kind under an environment $\G$.

% Type Equality
Type equality rules are needed because the type equivalence is not obvious unlike simply typed lambda calculus.
For example, $\textrm{Vector}\ 7$ should be equivalent to $\textrm{Vector}\ (3+4)$
but they are not equivalent seemingly. Thus, we must define equivalence rules.
In \LLF, equivalence is expressed with a symbol of $\E$.
$\G \vdash M \E N$ means a term $M$ and a term $N$ are equivalent under the environment $\G$.
$\G \vdash \tau \E \sigma$ means a type $\tau$ and a type $\sigma$ are equivalent under the environment $\G$.
$\G \vdash K \E J$ means a kind $K$ and a kind $J$ are equivalent under the environment $\G$.
